### 2018-10-17 Paper/revision/reviewer_replies.tex

Convergence behavior in this case depends upon the variability in the gradient of
$G(\theta)$ with respect to individual parameters, $\theta_i$ in their respective
domains. For the numerical tests and the application considered in this work, the
gradient is not observed to vary significantly in the considered domain of the
parameters. In other words, the variance of the estimator is low. 
Hence, a small number of Monte Carlo samples are able to estimate
the screening parameters. This is a common observation in many practical
applications, and therefore the proposed methodology involving an iterative
approach can yield significant computational savings.

These points have been emphasized in the discussion in Section~6 (Summary and
Conclusion) in the revised manuscript.

\item 
\referee{P17, Figure 3, what's the degree of the PCE used in the example? The same
question applies to Figure 6 and Figure 8.}

In the borehole test case, the degree of the PCE was found to be 3 in the reduced space (4D)
and 5 in the full space (7D). In the case of semilinear elliptic PDE, the degree of the PCE was 
found to be 3 in the reduced space (5D) as well as the original space (10D). For the reaction
kinetics application, the degree of the PCE was found to be 3 in the reduced space (4D) and 
2 in the full space (19D).

The captions of Figures 3, 6, and 8 have been updated to include this information.

\item
\referee{
P25, Figure 7, it seems that the rank of the parameters and the difference of
$\mu_s$ doesn't change too much over iterations. Does it indicate the initial
parameter screening  (line 1-6 in Algorithm 1) is good enough for ranking the
parameters? Can the authors plot the similar figure for other examples to see
if the iterative screening procedure does make a difference on the ranking the
parameters compared with the initial parameter screening step?}

The reviewer is correct in pointing out from Figure 7 that the initial screening step
reasonably approximates the screening metric. The is also observed in
Figure 5 for the semilinear elliptic PDE test case. It is also true in the borehole test
case and a similar figure has been included for this example in the revised manuscript
(Figure 2c) as suggested by the reviewer. The reason for this observation has already
been discussed in response to Comment~1 above and included in the revised manuscript.

\end{enumerate}

@@

\referee{
An adaptive surrogate model construction approach in reduced input parameter
space is proposed in this paper. Instead of variance based sensitivity indices,
derivative based global sensitivity measures are employed to calibration of the
important model inputs, upon which surrogate models are constructed. To
demonstrate the computational advantage, the proposed approach is then
validated against three examples.  The reviewer’s recommendation is ``major
revision''.}

Major comments:
\begin{enumerate}

\item
\referee{
In this paper, the constructed surrogate model is either a RSS or a FSS. Based
on the diagram on page 12, the resulting RSS is built upon the not sufficiently
accurate FSS model (which could lead the accuracy to decrease further), or
is the RSS constructed directly from the original model with reduced input
parameters? The diagram is ambigous on this issue.}

The reviewer correctly points out that the resulting surrogate model is either an RSS or
an FSS. However, we would like to clarify that the main purpose of the proposed
methodology is to construct an RSS based on estimates of the screening metric.
However, since estimating the metric requires model evaluations, we further exploit these
evaluations to construct an FSS (free of cost) using regression-based approaches 
mentioned in the paper. Note that the FSS construction is performed simultaneously to 
ensure that the computational effort associated with obtaining converged estimates of
the screening metric and RSS construction does not overshoot that required for
constructing a sufficiently accurate FSS.

The above points are already included in the paragraph on the discussion of the proposed
methodology in Section 3. Nevertheless, based on the reviewer's feedback, we have tried to
clarify and emphasize these points in the first paragraph in Section 6 (Summary and Conclusion)
in the revised manuscript.

@@

\item
\referee{The reviewer would also like to see the comparison of the computational cost
(not just the numerical results) of DGSMs to variance based sensitivity indices
with increasing parameter dimension, e.g. Sobol’ indices incorporated with
sparse grid, since the difference decreases with increasing number of parameters.}

\item 
\referee{In section 4 and 5, no predictive convergence using the test data sample is
presented, only the convergence of $\epsilon_\text{LOO}$, which reuses the training data as
the validation set, is shown. This shows only the convergence of the model,
and does not necessarily indicate the (predictive) accuracy of the constructed
model, hence could lead to false conclusion. The reviewer would like to see the
convergence of $\epsilon_{L_2}$.}

As suggested by the reviewer, the plots and related discussion pertaining to the convergence 
of $\epsilon_{L_2}$ have been included for the numerical tests presented in Section 3 and 
the chemical kinetics application presented in Section 4.

@@

\item 
\referee{How would the proposed approach behave when presented with severe nonlinearity
or rare events where the screening metrics could misrepresent the significance
of parameters?}

Severe non-linearity in the model output as a function of uncertain inputs could potentially lead
to a significantly large variability in its gradient. Hence, a large number of Monte Carlo samples might be
required to estimate the screening metrics with reasonable accuracy in this case depending upon the
application. Therefore, the computational effort is expected to increase in such cases. In the presence
of rare events, the variance-based approaches typically lead to inaccurate estimates of 
parametric sensitivities. Since the proposed methodology in this work aims to reduce the computational
effort pertaining to total-effect Sobol index which is a variance-based measure, it might lead to
inaccurate estimates of the screening metric and therefore, the relative importance of the. uncertain
inputs.

A brief discussion based on the above points has been included in Section 6 (Summary and Discussion).

@@

\item 
\referee{The reviewer would like to see some comments on the change of computational
cost of the proposed approach with respect to the increase of parameter dimensions.}
\end{enumerate}

Minor comments have also been addressed in the revised manuscript. The authors thank
the reviewer for pointing those out as well.

### 2018-10-17 Paper/app.tex
..

A reduced-space surrogate (RSS) was constructed in 4D for the fuel-rich case,
and in 3D for
the fuel-lean case. Figure~\ref{fig:err_samples_kinetics} illustrates a
comparison of convergence characteristics for the PCEs constructed in the
full-space and the reduced-space for the fuel-rich case. Note that the
plot is generated using the implementation of least angle regression (LAR)
for sparse PCEs in UQLab.  
%
\begin{figure}[htbp]
 \begin{center}
  \includegraphics[width=0.48\textwidth]{./Figures/err_samples_kinetics}
\caption{A semi-log plot of $\epsilon_\text{\tiny LOO}$ as a function of
number of model evaluations in the full-space (19D) and the reduced-space (4D)
for the fuel (H$_2$)-rich case i.e. $\phi$ = 2.0.}
\label{fig:err_samples_kinetics}
\end{center}
\end{figure}
%
The leave-one-out cross validation error is observed to drop initially
and plateau with the increase in training points for the 19-dimensional
PCE. However, in the case of 4-dimensional PCE, the error exhibits a
monotonic behavior and is found to be smaller than $\mathcal{O}(10^{-5})$
at 60 training points. Clearly, the RSS shows a much faster rate of convergence.
Similar trends (not included) were observed in the fuel-lean case.

Based on $\epsilon_{\mbox{\tiny{L-2}}}$ estimates using the 
cross-validation set, the RSS was found to be accurate within 1.8$\%$ in the
fuel-rich case, and
within 3.1$\%$ in the fuel-lean case. Model evaluations at 1000 samples in the test suite
are further used to plot a normalized histogram of the ignition time in 
Figure~\ref{fig:pdf_kinetics}. To verify the accuracy of the RSS in a 
probabilistic-sense, we compare the histogram plot with a PDF of ignition time
using surrogate predictions at 10$^{6}$ samples in the reduced space in both cases. 
%
\begin{figure}[htbp]
 \begin{center}
  \includegraphics[width=0.48\textwidth]{./Figures/pdf_comp_rich}
  \includegraphics[width=0.48\textwidth]{./Figures/pdf_comp_lean}
\caption{A normalized histogram based on model evaluations at 1000 samples is plotted
along with a PDF of ignition delay for the fuel-rich case (left) and the fuel-lean
case (right).}
\label{fig:pdf_kinetics}
\end{center}
\end{figure}
%
Clearly, the RSS captures the spread as well as the modal estimate of
the ignition delay in both scenarios. Hence, the proposed framework 
has enabled significant dimension reduction and construction of an accurate
RSS for multiple scenarios pertaining to the H$_2$/O$_2$ reaction
mechanism.

>>>>

A reduced-space surrogate (RSS) was constructed in 4D for the fuel-rich case,
and in 3D for
the fuel-lean case. Figure~\ref{fig:err_samples_kinetics}~(left) illustrates a
comparison of convergence characteristics for the PCEs constructed in the
full-space and the reduced-space for the fuel-rich case. Note that the
plot is generated using the implementation of least angle regression (LAR)
for sparse PCEs in UQLab.  
%
\begin{figure}[htbp]
 \begin{center}
  \includegraphics[width=0.45\textwidth]{./Figures/err_samples_kinetics}
   \includegraphics[width=0.44\textwidth]{./Figures/errL2_samples_kinetics}
\caption{Left: A semi-log plot of $\epsilon_\text{\tiny LOO}$ as a function of
number of model evaluations in the full-space (19D) and the reduced-space (4D)
for the fuel (H$_2$)-rich case i.e. $\phi$ = 2.0. \rebut{The degree of
the resulting PCE was found to be 3 and 2 in the 4D and the 19D case respectively.
Right: Semilog plot of the relative L-2 error norm ($\epsilon_{\mbox{\tiny{L-2}}}$)
for the PCEs constructed in 4D and 19D.}}
\label{fig:err_samples_kinetics}
\end{center}
\end{figure}
%
The leave-one-out cross validation error is observed to drop initially
and plateau with the increase in training points for the 19-dimensional
PCE. However, in the case of 4-dimensional PCE, the error exhibits a
monotonic behavior and is found to be smaller than $\mathcal{O}(10^{-5})$
at 60 training points. Clearly, the RSS shows a much faster rate of convergence.
\rebut{Additionally, the
convergence of the relative error norm, $\epsilon_{\mbox{\tiny{L-2}}}$ in 
Figure~\ref{fig:err_samples_kinetics}~(right) indicates that for the case of 10
samples, the 4D PCE is observed to be more accurate. However, the 19D PCE
is observed to be more accurate by an order of magnitude as the sample size
increases. Specifically, the 4D PCE was found to be accurate within 1.8$\%$ in the
fuel-rich case, and within 3.1$\%$ in the fuel-lean case. Therefore, the 4D PCE
is still observed to be reasonably accurate in this case. Moreover, its faster convergence
as mentioned earlier should help reduce computational effort associated with
surrogate model construction.}
Similar trends (not included) were observed in the fuel-lean case.

Model evaluations at 1000 samples in the test suite
are further used to plot a normalized histogram of the ignition time in 
Figure~\ref{fig:pdf_kinetics}. To verify the accuracy of the RSS in a 
probabilistic-sense, we compare the histogram plot with a PDF of ignition time
using surrogate predictions at 10$^{6}$ samples in the reduced space in both cases. 
%
\begin{figure}[htbp]
 \begin{center}
  \includegraphics[width=0.48\textwidth]{./Figures/pdf_comp_rich}
  \includegraphics[width=0.48\textwidth]{./Figures/pdf_comp_lean}
\caption{A normalized histogram based on model evaluations at 1000 samples is plotted
along with a PDF of ignition delay for the fuel-rich case (left) and the fuel-lean
case (right).}
\label{fig:pdf_kinetics}
\end{center}
\end{figure}
%
Clearly, the RSS captures the spread as well as the modal estimate of
the ignition delay in both scenarios. Hence, the proposed framework 
has enabled significant dimension reduction and construction of an accurate
RSS for multiple scenarios pertaining to the H$_2$/O$_2$ reaction
mechanism.

### 2018-10-17 Paper/disc.tex
..

In this work, we have presented an efficient and practical approach for constructing
a reduced-space
surrogate for scientific and engineering applications. Dimension reduction is accomplished
by identifying uncertain parameters that contribute relatively less towards the uncertainty
in the quantity of interest. These parameters deemed as \textit{unimportant} are determined
using a screening metric~\eqref{eq:cmu} involving derivative-based sensitivity
measures. Initially, the metric is estimated
using model evaluations at a small set of samples in the parameter domain. These
estimates are refined by subsequent enrichment of the sample set during the screening
procedure presented in Algorithm~\ref{alg:screen}. The outcome of parameter screening is
assessed for the scope of dimension reduction. In a favorable scenario, a reduced-space
surrogate (RSS) is constructed. The RSS is tested for accuracy in a least-squares sense
as well as a probabilistic sense using a cross-validation test suite. In the proposed framework,
a surrogate in the full-space (FSS) is constructed in tandem with parameter screening using
the available set of model evaluations. Both, RSS and FSS are
constructed using regression-based sparse PCEs. Simultaneous construction
of the FSS ensures that the computational effort associated with the proposed framework
does not overshoot the effort required to construct the FSS directly.
Hence, the RSS is constructed only in situations where computational gains are
expected.

@@

Based on the results presented for the test problems and the kinetics
application, the proposed framework seems quite promising in its
potential for identifying the unimportant model inputs. \rebut{In fact, in 
the numerical tests and the chemical kinetics application presented in this
work, reasonable estimates of the screening metric are obtained during the
initial screening step with only 5 samples. This is indicative of a small
degree of
variability in the gradient of the model output with respect to individual
parameters, and therefore, a low variance of the Monte Carlo estimator.}
These observations could be exploited to construct efficient model surrogates
in a reduced input space. However, it is important to remain cognizant
about the limitations of the framework as well. 
For instance, the quantity of interest is required to be differentiable with
respect to each parameter in the considered domain. This condition once
satisfied, enhances the accuracy of the PCE-based surrogates as well.  
Additionally, the proposed framework does not
account for the existence of possible correlations between the uncertain
inputs of the model. However, while the assumption of independent
inputs is not always justified, in many cases, correlations between
inputs are not well understood a priori, and assuming mutual independence
could be reasonable at least in initial screening using DGSMs. On the other
hand, if approximate correlations are known, we recommend using a Gaussian 
process or Kriging-based surrogate since it 
provides a means for incorporating the correlation between inputs.  
Implementation to applications involving strongly correlated parameters
could enhance the applicability of the proposed framework. 
We consider that to be a potential direction for future studies related
to this work.

>>>>

In this work, we have presented an efficient and practical approach for constructing
a reduced-space
surrogate for scientific and engineering applications. Dimension reduction is accomplished
by identifying uncertain parameters that contribute relatively less towards the uncertainty
in the quantity of interest. These parameters deemed as \textit{unimportant} are determined
using a screening metric~\eqref{eq:cmu} involving derivative-based sensitivity
measures. Initially, the metric is estimated
using model evaluations at a small set of samples in the parameter domain. These
estimates are refined by subsequent enrichment of the sample set during the screening
procedure presented in Algorithm~\ref{alg:screen}. The outcome of parameter screening is
assessed for the scope of dimension reduction. In a favorable scenario, a reduced-space
surrogate (RSS) is constructed. The RSS is tested for accuracy in a least-squares sense
as well as a probabilistic sense using a cross-validation test suite. In the proposed framework,
a surrogate in the full-space (FSS) is constructed in tandem with parameter screening using
the available set of model evaluations. Both, RSS and FSS are
constructed using regression-based sparse PCEs. \rebut{Note however that the FSS is
constructed in an independent manner to ensure that the computational effort associated
with the proposed methodology does not overshoot the effort required to construct the 
FSS directly. Therefore, it does not impact the accuracy of the RSS which is only
constructed in situations where computational gains are expected.}

@@

Based on the results presented for the test problems and the kinetics
application, the proposed framework seems quite promising in its
potential for identifying the unimportant model inputs. \rebut{In fact, in 
the numerical tests and the chemical kinetics application presented in this
work, reasonable estimates of the screening metric are obtained during the
initial screening step with only 5 samples. This is indicative of a small
degree of
variability in the gradient of the model output with respect to individual
parameters, and therefore, a low variance of the Monte Carlo estimator.}
These observations could be exploited to construct efficient model surrogates
in a reduced input space. However, it is important to remain cognizant
about the limitations of the framework as well. 
For instance, the quantity of interest is required to be differentiable with
respect to each parameter in the considered domain. This condition once
satisfied, enhances the accuracy of the PCE-based surrogates as well.  
\rebut{Moreover, in the presence of severe non-linearities in the model output
leading to significant variability in its gradient in the considered input domain,
the number of samples and hence, the computational effort associated with
the estimation of screening metrics would expectedly 
increase. The extent of increase in the effort would of course depend upon the
application. In the case of rare events, the variance-based methods typically
lead to inaccurate estimates of the uncertainty in the model output. Since the
methodology proposed in this work is based on reducing computational
effort associated with variance-based sensitivity analysis, specifically, the
total-effect Sobol' index, it might lead to erroneous estimates of the
screening metrics and consequently the relative importance of the
uncertain parameters.}
Additionally, the proposed framework does not
account for the existence of possible correlations between the uncertain
inputs of the model. However, while the assumption of independent
inputs is not always justified, in many cases, correlations between
inputs are not well understood a priori, and assuming mutual independence
could be reasonable at least in initial screening using DGSMs. On the other
hand, if approximate correlations are known, we recommend using a Gaussian 
process or Kriging-based surrogate since it 
provides a means for incorporating the correlation between inputs.  
Implementation to applications involving strongly correlated parameters
could enhance the applicability of the proposed framework. 
We consider that to be a potential direction for future studies related
to this work.
